State of the Practice for Lattice Boltzmann Method Software

### 2022-01-27 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Revisions to Section 3.8 on Reusability

We measured the total number of source code files for each project. A larger
number of source files is associated with increased reusability, due to our
assumption that this indicates increased modularization. Some packages have more
features than others.  This is assumed to contribute to reusability, since they have
more source code for potential reuse. The software packages were also reviewed
for the presence of API documentation, which indicates that a software package
was developed with interaction between other software applications in mind.

@@

Figure~\ref{Fig_Reusabilty} shows the reusability ranking of the software
packages using AHP. Software packages with a high score have thousands of source
code files and API documentation. The highest scoring packages, ESPResSo and
waLBerla, have extensive functionality, including graphical visualizations and
non-LBM modeling. For this reason, a comparison with other software packages is
not on a level field. However, these packages do have an abundance of reusable
components. Furthermore, nine of the top 10 ranked packages are noted as being
alive. HemeLB is considered to be dead.

@@

There was a strong focus on modularity when designing the waLBerla framework to
enhance productivity, reusability, and maintainability
\citep{bauer2021walberla}. The design of waLBerla has enabled it to be
successfully applied in several projects as a basis for various extensions
\citep{bauer2021walberla}.

@@

>>>>

We measured the total number of source code files for each project. We assume
that a large number of source files is associated with increased reusability,
due to our assumption that this indicates increased modularization. Some
packages have more features than others.  This is assumed to contribute to
reusability, since they have more source code for potential reuse. The software
packages were also reviewed for the presence of API documentation, which
indicates that a software package was developed with interaction between other
software applications in mind.

@@

Figure~\ref{Fig_Reusabilty} shows the reusability ranking of the software
packages. Software packages with a high score have thousands of source code
files and API documentation. The highest scoring packages, ESPResSo and
waLBerla, have extensive functionality, including graphical visualizations and
non-LBM modeling. For this reason, a comparison with other software packages is
not on a level field. However, these packages do have an abundance of reusable
components. Nine of the top 10 ranked packages are noted as being alive.

@@

The package waLBerla scored high on reusability because of its focus on
modularity.  The modularity in the waLBerla framework was included to enhance
productivity, reusability, and maintainability \citep{bauer2021walberla}. The
design of waLBerla has enabled it to be successfully applied in several projects
as a basis for various extensions \citep{bauer2021walberla}.

@@

The assumption that more code files is an indicator of reusability
(Section~\ref{reusabilityresults}) may not be a valid assumption.
